Supplemental Details

### 2016-10-29 Supplement.Rmd
edited rough draft. added figure descriptions
clean house

@@

1. **Collect all posts and comments from /r/depression in June 2016. **
We use the package subredditarchive, and modify the existing code from the python script here: https://github.com/peoplma/subredditarchive. The modified code that we used to scrape the June data can be found in 
[Scripts/0_Scrape_June_Data.py](Scripts/0_Scrape_June_Data.py).
Parse the json files for each thread for the main post and comments. For each, grab information on author, title (if applicable), text, creation date, name/link id, etc. 
(See code: [Scripts/1_Read_Json_Files.R](Scripts/1_Read_Json_Files.R))

@@

3. **Scrape Author Data.**
Collect all available post and comment data for every SI-positive authors. Collect all available post and comment data for a similar-sized simple random sample of SI-negative authors. We collected ours at 4pm on October 10, 2016.
(See code: [Scripts/3.1_Scrape_User_Data.R](Scripts/3.1_Scrape_User_Data.R) and
[Scripts/3.2_Scrape_NoSI_User_Data.R](Scripts/3.2_Scrape_NoSI_User_Data.R))

4. **Drop-Out Estimation.** Estimate the expected number of drop-outs attributable to SI. 
(See derivation: [Estimation of Drop-Out Totals](#estimation-of-drop-out-totals), 
see code: [Scripts/6_MC_Estimation.R](Scripts/6_MC_Estimation.R))

5. If a bayesian approach was used, examine the relationship between the estimate and the priors.

# Estimation of Drop-Out Totals

Derivation:

Let $i$ index the authors. Let $Q_i$ be the (unobserved) event that author $i$ has quit Reddit. Let $t_i$ be the time since observing the most recent post from author $i$. Let $y_i$ be the (unobserved) length of time from the most recent post to the next post in the future. If author $i$ has quit Reddit, then $y_i = \infty$. Let $n_i$ be the observed number of intervals between posts for author $i$. Let $\bar{\epsilon_i}$ be the observed average time between Reddit posts for author $i$. Let $SI_i$ be the (unobserved) indicator that author $i$ dropped off of Reddit. Let $\rho$ be the prior probability (which we define) that any author drops out of Reddit.

Our goal is to do monte-carlo sampling from the posterior distribution of 
$E(\sum_i Q_i | SI_i=1) - E(\sum_i Q_i | SI_i=0)$.

First assume that the post histories of each author are a Poisson process, and so observed times between posts are exponentially distributed with parameter $\lambda_i$. For each $\lambda_i$, specify the prior distribution $\lambda_i \sim gamma(1,1)$. 
Hence the posterior for $\lambda_i$ is 
$\lambda_i \big |n_i,\bar{\epsilon_i} \sim gamma(n_i + 1, 1 + n_i\cdot\bar{\epsilon_i})$. [CITE RESULT].

Given $\lambda_i$ and prior $\rho$, we are able to calculate the probability that the author has stopped using Reddit using Bayes Rule.
$$ P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)
            =  \frac{P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) \cdot \rho}
                        {P(y_i > t_i|\lambda_i, t_i, \rho)}
            =   \frac{\rho} {e^{-\lambda_i\cdot t_i} \cdot (1-\rho) + \rho} 
$$ 
Note that $P(y_i > t_i| Q_i, \lambda_i, t_i, \rho) = 1$ since $y_i = \infty$ for the event $Q_i$. Also note that marginal to $Q_i$, $y_i$ follows a mixture of infinity with probability $\rho$ and an exponential with parameter $\lambda_i$ and probability $\rho$.

Now, if we consider each $Q_i$ to be independent, and we are given $P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$ for each author, then 
$$E(\sum_i Q_i| SI_i = 1) - E(\sum_i Q_i| SI_i = 0) = 
      \sum_i (-1)^{SI_i +1} P(Q_i|\lambda_i, y_i > t_i, t_i, \rho)$$

Hence, using these formulas, we can generate monte-carlo samples from the posterior distribution for the expected number of drop-outs attributable to SI.

@@

@@

>>>>

```{r setup, message=FALSE, echo=FALSE}
library(ggplot2)
library(dplyr)
library(chron)
library(lubridate)
options(width = 200)
```

@@

1. **Collect all posts and comments from /r/depression in June 2016. **
We use the package subredditarchive, and modify the existing code from the python script here: https://github.com/peoplma/subredditarchive. The modified code that we used to scrape the June data can be found in 
[Scripts/0_Scrape_June_Data.py](Scripts/0_Scrape_June_Data.py).
We parse the json files for each thread for the main post and comments. For each, grab information on author, title (if applicable), text, creation date, name/link id, etc. 
(See code: [Scripts/1_Read_Json_Files.R](Scripts/1_Read_Json_Files.R))

@@

```{r, message=FALSE}
load(file = "Data/June_Depression_Sample/June_Posts_Classified.RData")
user.data$author[user.data$author == "\\[deleted\\]"] = NA
user.data$text[grepl("\\[deleted\\]",user.data$text)] = NA
summarise(user.data,
          total_posts = n(),
          total_si = sum(si),
          total_authors_si = length(unique(author[si])),
          unique_authors = length(unique(author)),
          unique_threads = length(unique(thread_id)))
authors = with(user.data, unique(author[si])) %>% na.omit()
authors.noSI = with(user.data, unique(author[!si])) %>% na.omit() %>% sample(500)
length(authors); length(authors.noSI)
rm(authors, authors.noSI, user.data)
```

3. **Scrape Author Data.**
Collect all available post and comment data for every SI-positive authors. Collect all available post and comment data for a similar-sized simple random sample of SI-negative authors. We collected ours at 4pm on October 10, 2016. 
We user this code to scrape the author data: [Scripts/3.1_Scrape_User_Data.R](Scripts/3.1_Scrape_User_Data.R),
[Scripts/3.2_Scrape_NoSI_User_Data.R](Scripts/3.2_Scrape_NoSI_User_Data.R). 
It takes nearly 24 hours to run. 
We use this code to classify the comments as SI-expressive:
[Scripts/4.1_Classify_SI_Author_Data.R](Scripts/4.1_Classify_SI_Author_Data.R),
[Scripts/4.2_Classify_NoSI_Author_Data.R](Scripts/4.2_Classify_NoSI_Author_Data.R).
This takes ~30 minutes to run. 
We use this code to combine the data and format it for plots, as well as summarize it for the estimation: 
[Scripts/5_Combine_Authors.R](Scripts/5_Combine_Authors.R).

```{r}
load("Data/SI_Author_Sample/June_Authors_Combined.RData")
user.data %>%
      group_by(si.author) %>%
      summarise(
          n_author = length(unique(author)),
          n_posts = n(),
          posts_per_author = n_posts / n_author,
          n_posts_si = sum(class, na.rm=T))
```

4. **Drop-Out Estimation.** Estimate the expected number of drop-outs attributable to SI. We save the posterior samples to plot in the paper.
(See code: [Scripts/6_MC_Estimation.R](Scripts/6_MC_Estimation.R))

@@

A number of methods have been implemented to detect suicidal ideation from user-generated text on social media [1]. However, here we use a simpler algorithm and leave the implementation of these other classifiers as a future project.

We expected SI expression to be fairly rare among /r/Depression posts. Thus, in order to get a good estimate of the drop out risk attributable to SI, we wanted our SI-positive sample to have a minimal proportion of true SI-negative authors. However, we were not worried about true SI-positive authors tainting our SI-negative sample since we expected SI-positive author to be so rare, and hence not have much influence on our estimate of the SI-negative drop out risk. In other words, we wanted a highly specific algorithm at the sacrifice of sensitivity.

To achieve this goal, we implement an algorithm that searches post text for at least one phrase from a reference list of SI-expressive phrases. We generated our reference list by programatically expanding a sample of SI-expressive phrases which were hand-picked from 750 random June /r/Depression comments. The algorithm is detailed in [Supplement/SI Classification](Supplement.html).

@@

##### SI Classification: PPV & NPV

We use the script [Scripts/99_Assign_Test_Values.R](Scripts/99_Assign_Test_Values.R) to sample 200 posts and hand-classify them as having true SI or not.

```{r ppv, message = FALSE, warning=FALSE}
load(file = "Data/Test/Test_Classified.Rdata")
colnames(test.sample)
with(test.sample, table(si, suicidal))
library(Hmisc)
binconf(c(88, 96), c(100, 100), alpha=0.05, method=c("exact"))
```

We can see that the positive predictive value is 88% and the negative predictive value is 96%.
